Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-25 VMCAI-revised-version/final.tex
up

>>>>

The structural termination problem consists in deciding if the termination problem holds for  for every initial state. Since termination is w.l.o.g. reachability of $q_f({\bf 0})$ for some control state $q_f$, we can formulate the structural termination problem as

\problemx{Structural termination}
{A reset-VASS $V=(Q,T)$ of dimension $d$, a control state $q_f \in Q$.}
{ $Q \times \longrightarrow^{*} q_f({\bf 0})$ ? \\}
